%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Bennett}{Rand}{ % Your name
\urlstyle{same}\url{http://bennett-rand.com} \\ % Your website, LinkedIn profile or other web address
\href{mailto:bennett.h.rand@gmail.com}{bennett.h.rand@gmail.com} | (925)336-0995 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Oregon State University}

\descript{B.S. Computer Science}
\location{June 2014 | Corvallis, OR}
Applied Computer Science Program \\
School of Electrical Engineering and Computer Science \\
%\location{Major GPA: 3.32 / 4.0}

%\sectionspace % Some whitespace after the section

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/BennettRand}{\bf BennettRand} \\
LinkedIn:// \href{https://www.linkedin.com/pub/bennett-rand/51/76a/679}{\bf Bennett Rand} \\
%Twitter:// \href{https://twitter.com/Bennett_Rand/}{\bf @Bennett\_Rand} \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

%\subsection{Undergraduate}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightitemize}
\item Computer Arch and Assembly Lang
\item Operating Systems I \& II
\item Software Engineering I \& II
\item ST/ HCI Research Methods
\item Digital Logic Design
\item Intro to Usability Engineering
\item Computer Org \& Assembly Lang
\item Intro Artificial Intelligence
\item ST/ Intro to Info Visualization
\item Computer Architecture
\item Applied Robotics
\item Machine Learning \& Data Mining
\item Intro to Parallel Computing
\item Network Security
\item Mobile/Cloud Development
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Languages}

\location{Strong:}
Python \textbullet{} Go \textbullet{} C \textbullet{} C++\\
JavaScript \textbullet{} SQL \textbullet{} HTML \& CSS\\
\location{Familiar:}
Assembly (AVR, x86, ARM v6)\\
C\# \textbullet{} Java \textbullet{} PHP \\

\subsection{Other}
AWS \textbullet{} Ansible \textbullet{} Cassandra \textbullet{} Consul \\
Django \textbullet{} ELK \textbullet{} Flask \textbullet{} Git \textbullet{} Jenkins CI \\
Linux \textbullet{} Mesh Networking \textbullet{} MySQL \\
PostgreSQL \textbullet{} Protocol Buffers \textbullet{} Redis \\
Solaris \textbullet{} WebSockets \textbullet{} Windows

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%----------
%Interests
%----------

\section{About}
I am a software engineer specializing in writing efficient Python and Go for low-level embedded environments and scalable backend systems.
I have experience with AWS, microservices, Internet of Things, wireless sensor networks, and green energy.\\[1em]
I am happiest building things that other people enjoy using, especially when it aligns with my other hobbies.
\sectionspace

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Ditto.com}
\descript{| Backend Software Engineer}

\location{January 2017 - Current | San Francisco, CA}
I support and implement a cloud-based 3D rendering and face-scanning service on AWS. The service provides "Virtual Try-Ons" to eyewear e-commerce businesses.\\[1em]
My responsibilities include designing and implementing databases and APIs, diagnosing and improving performance, working with DevOps to deploy products at scale, creating internal and customer-facing tools, mentoring new employees, and participating in the on-call cycle.\\[1em]
Recently I helped lead a team in designing the architecture and implementation of a horizontally scalable, distributed image and video processing system on AWS. Some challenges were real-time scaling based upon current demand, reloading configuration without downtime, monitoring, synchronizing states between nodes, and formatting easily-searchable logs. All components in the new system have been well documented and diagrammed to allow future and current developers to easily take part in any further development of the system.
\sectionspace

Technology Used:\\
\begin{tabular}{llll}
AWS & Django & PostgreSQL & S3\\
Ansible & Flask & Protocol Buffers & SQS\\
Consul & OpenCV & Redis & Twisted\\
\end{tabular}

\sectionspace % Some whitespace after the section

%---------------------------------------------------

\runsubsection{SolarCity}
\descript{| Embedded Software Engineer}

\location{September 2014 - August 2016 | San Mateo, CA}

I maintained and added new features to a Python application that ran on small, Linux-powered, embedded devices.
The application communicated to various power appliances in order to send power data samples back to a database and a real-time messaging system.
It also controlled various settings on the appliance when commanded over the real-time messaging system.\\[1em]
I also spearheaded the effort to get the Python application's build process off of developers' computers and into continuous integration with unit testing,
as well as move away from using a SQL-based logging system to using a third-party log management stack.
\sectionspace

Technology Used:\\
\begin{tabular}{llll}
Cassandra & Git & MSSQL & TCP/IP\\
ELK & Jenkins CI & RS-485 & WebSockets\\
Flask & MODBUS & RabbitMQ & ZigBee (802.15.4)\\
\end{tabular}

\sectionspace % Some whitespace after the section

%---------------------------------------------------

% \runsubsection{Oregon State University EECS}
% \descript{| Undergraduate TA}

% \location{Spring 2012 – Spring 2014 | Corvallis, OR}
% I ran lab sections, graded exams, held office hours, held assignment demonstrations, and graded assignments for multiple classes.
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
% \begin{tightitemize}
% \item Operating Systems II (1 Quarter): Mr. D. Kevin McGrath
% \item Computer Arch. and Assembly Language (1 Quarter): Mr. D. Kevin McGrath
% \item Operating Systems I (3 Quarters): Mr. D. Kevin McGrath
% \item Intro to Computer Science II (6 Quarters): Mr. Donald Heer, Mr. D. Kevin McGrath, Dr. Jennifer Parham-Mocello, and  Dr. Weng-Keen Wong
% \end{tightitemize}

% \sectionspace % Some whitespace after the section

%------------------------------------------------

%\runsubsection{The Athenian School}
%\descript{| Summer Camp Instructor}

%\location{Summer 2011 | Danville, CA}
%I taught a Lego robotics course to elementary school children. I designed the course and created the syllabus and lab exercises. We provided hands-on experience with both Lego Mindstorms NXT and RCX, programmed in RoboLab (based upon NI LabView). After starting with basic mechanism design, we finished with a challenge of a line-following maze.

%\sectionspace % Some whitespace after the section

\hfill \location{Continued on next page.}

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
\begin{minipage}[t]{0.99\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}

\runsubsection{Dr. Wattson}
\descript{| Senior Capstone Project (Award-Winning)}

\location{Fall 2013 - Spring 2014 | \href{http://goo.gl/PqPYvQ}{http://goo.gl/PqPYvQ}}
Designed and built a mesh network of power monitors to measure home power usage patterns and help people conserve energy.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Samplify}
\descript{| A Python Library for Physical Measurements}

\location{2016 | \href{https://github.com/BennettRand/Samplify}{https://github.com/BennettRand/Samplify}}
A library to keep track of magnitude and unit-aware measurements.
The purpose is to simplify the manipulation of physical quantities and ensure incompatible units are not confused with each other.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Cause and Affect Microdonations}
\descript{| Easy Socal Non-Profit Donations}

\location{March 2017 | \href{https://causeandaffect.net/}{https://causeandaffect.net/}}
A donation platform built on AWS to facilitate non-profit fundraising within the Twitch livestreaming ecosystem.

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards} 

\begin{tabular}{rll}
2014	 & Second Place & Engineering Expo. Industry Award, Oregon State University\\
2014	 & Honorable Mention & Cornell Cup USA, Presented by Intel\\
2013	 & Finalist & Cornell Cup USA, Presented by Intel\\
2009	 & Regional Winner & FIRST Robotics Competition, Silicon Valley Regional\\
\end{tabular}

\sectionspace % Some whitespace after the section

\section{References available upon request.}

%\section{Example Section 2}

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}